---
title: "Weekly Summary Template"
author: "Marc Hughes"
title-block-banner: true
title-block-style: default
toc: true
# format: html
format: pdf
---

---

## Tuesday, Feb 7

::: {.callout-important}
## TIL

Include a _very brief_ summary of what you learnt in this class here. 

Today, I learnt the following concepts in class:

1. Interpretation of regression coefficients
1. How to do regression with categorical covariates
1. How to relevel/reorder the baseline level
:::

Provide more concrete details here. You can also use footenotes[^footnote] if you like

```{R results='hide'}
#| output: false
library(tidyverse)
```



In class we were shown how to relevel the baseline level using the 'relevel()' function.


```{r}
# before
iris$Species
iris$Species <- relevel(iris$Species, "virginica")

# after
iris$Species
```



## Thursday, Feb 9



::: {.callout-important}
## TIL

Include a _very brief_ summary of what you learnt in this class here. 

Today, I learnt the following concepts in class:

1. What 'names spaces' are how they allow for the calling of repeat function names across different packages
1. I learned that if we have a high R Squared then the p-value is significant but a significant p-value does not guarantee a high R Squared
1. I learned how to do multiple regression with categorical covariates.
:::

I learned about the interpretation for coefficients in a regression model with multiple covariates.

```{R}
library(ISLR2)
attach(Credit)

df<- Credit %>%
  tibble()
df

df3 <- df %>% select(Income, Rating, Limit)
df3
```


```{r}
model <- lm(Limit ~ Income + Rating, df3)
model
```

1. $\beta_0$ is the expected value of $y$ when $income = 0$ and $rating = 0$

2. $\beta_1$ is saying that if $rating$ is held constant and $income$ changes by 1 unit, then the corresponding change in the 'limit' is $0.5573$

3. $\beta_2$ is saying that if 'income' is held constant and 'rating' changes by $1$ unit, then corresponding change in 'limit' is $14.771$



[^footnote]: You can include some footnotes here